---
title: "6306_Project1_Zwei Group"
author: "Elisabet Zidow, Jonathan Franks, Shanqing Gu"
date: "2/18/2018"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Each State contains its own unique drinking culture. Our Zwei Analytics attempts to review the available 2410 craft beers and 558 breweries in the United States in order to explore this culture. There are two common beer measurements: Alcohol by Volume (ABV) and International Bitterness Unit (IBU). Rather than telling us how much alcohol there is like ABV, IBU measures the bitterness from hops in a beer on a scale of 0 to 100. Here, we provide the answers to these main questions and help you make your own own judgements about each states drinking culture : (1) How many breweries are present in each state? (2) What are the median ABV and IBU values for each state? (3) Which state has the maximum ABV or IBU beer? (4) Is there an relationship between the ABV and IBU?  

## Q1: How many breweries are present in each state?

In order to address this question, we use the dataset containing 558 breweries to rank and plot the breweries by state with decreasing order. From the plot, we can see the diversity of brewery distribution in each state. Briefly, Colorado (CO) state has 47 breweries, the highest number among all states. California (CA) and Michigan (MI) follows Colorado (CO) in brewery numbers, while Washington DC (DC), Sotuh Dakota (SD), North Dakota (ND), Wyoming (WY) have only one brewery in each state.  

```{r q1}
breweries <- read.csv("/Users/shanqinggu/Desktop/6306_Project_01/Breweries.csv", header=TRUE)
str(breweries)
head(breweries)
summary(breweries)

library("plyr")

breweries.count <- as.data.frame(table(breweries$State))
head(breweries.count)

breweries.order <- breweries.count[order(breweries.count$Freq, decreasing=TRUE),]
head(breweries.order)

breweries.order$Var1 <- factor(breweries.order$Var1, levels = breweries.order$Var1[order(breweries.order$Freq)])
breweries.order$Var1

library(ggplot2)

freq.plot <- ggplot(data=breweries.order, aes(x=Var1, y=Freq))+ 
  geom_bar(stat="identity", color="grey", fill="light blue")+
  geom_text(aes(label=Freq), hjust=-0.5, color="purple", position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  labs(title="Number of Craft Breweries in the United States (by each state)", x="State", y="Number of Craft Breweries")
  
freq.plot + coord_flip()
```

# Q2: What are the median ABV and IBU values for each state?

For this question, first we need to merge beer data with breweries data by Brew_ID. Use the firt and last six observations to check the merged file.

```{r q2}
beers <- read.csv("/Users/shanqinggu/Desktop/6306_Project_01/Beers.csv", header=TRUE)
str(beers)
head(beers)
dim(beers)
summary(beers)

colnames(beers)[5] <- "Brew_ID"
head(beers)

beer.merge <- merge.data.frame(beers, breweries, by="Brew_ID", all=FALSE)
head(beer.merge, 6)
tail(beer.merge, 6)
dim(beer.merge)
```

# 

Secondly, we need to report the numbers of NA's in each column. There are 62 NAs in the ABV column, while 1005 in the IBU column. 

```{r q3}
colSums(is.na(beer.merge))
```

# 

lastly, we compute and plot the median ABV and IBU for each state to compare by the SummaryBy statement in doBy libarary.

```{r q4}

library(doBy)

bar.median <- summaryBy(ABV+IBU~State,data=beer.merge, FUN=median, na.rm=TRUE)
dim(bar.median)
bar.median

bar.median.ABV <- bar.median[order(bar.median$ABV.median, decreasing=TRUE),]
bar.median.IBU <- bar.median[order(bar.median$IBU.median, decreasing=TRUE),]

barplot(bar.median.ABV$ABV.median, las=2, horiz=TRUE, 
        main = "The Median Alcohol Content for Each State", 
        xlab = "The Median Alcohol Content (ABV)", 
        col=rgb(0.2,0.4,0.6,0.6),
        names.arg=(bar.median$State), font=1,
        cex.axis=0.75, cex.names =0.75,
        xlim = c( 0, 0.07))
title(ylab="State", mgp=c(3,1,0), cex.lab=1.2)

barplot(bar.median.IBU$IBU.median, las=2, horiz=TRUE, 
        main = "The International Bitterness Unit for Each State", 
        xlab = "The International Bitterness Unit (IBU)", 
        col=rgb(0.2,0.4,0.6,0.6),
        names.arg=(bar.median.IBU$State), font=1,
        cex.axis=0.75, cex.names =0.75,
        xlim = c( 0, 50))
title(ylab="State", mgp=c(3,1,0), cex.lab=1.2)
```

# Q3  Which state has the maximum ABV or IBU beer? 

Use which.max function to find the state to have the maximum ABU and IBU beer.  As shown below, Colorado (CO) has the highese ABU beer and Oregon has the hight IBU beer.

```{r q5}
ABV.Max <- beer.merge[which.max(beer.merge$ABV),]
ABV.Max

IBU.Max <- beer.merge[which.max(beer.merge$IBU),]
IBU.Max
```

# 
From the summary statistics for the ABV variable, we can check the deta details: n, mean, sd, median, min, max, range and so on.

```{r q6}

library(psych)
describe(beer.merge$ABV)
```

# Q4 Is there an relationship between the ABV and IBU? 

The scatterplot and regression line support a strong positive correlation between ABV and IBU. 

```{r q7}
library(ggplot2)
beer.merge <- na.omit(beer.merge)
ggplot(data = beer.merge, na.rm=TRUE) + 
  geom_point(mapping = aes(x = ABV, y = IBU, color = beer.merge$State))+
  labs(title="Relationship between bitterness of the beer (IBU) and its alcoholic contents (ABV) with scatter plot", 
      x="Alcoholic contents (ABV)", y="Bitterness of the Beer (IBU)")

lm.fit <- lm(IBU ~ ABV, data = beer.merge)
summary (lm.fit)

plot(IBU~ABV, data=beer.merge,col = beer.merge$Style, main="IBU & ABV with Style")
abline(lm.fit)
cor.test(beer.merge$ABV, beer.merge$IBU)
```

# Completing the tale: Cause vs Correlation?

While the regression line and Pearson's correlation statistic show a strong positive relationship between ABV and IBU, it is clear that there is a lot of variance in IBU's across ABV.  We see that some Styles of beer group together there is still variance.  In fact, some beer Styles show significant variation in their IBU and ABV, suggesting that there is another factor.  
And that factor is sugar...
https://learn.kegerator.com/raising-abv/
Alcohol is a byproduct of the fermentation process, which takes place when the yeast converts the sugars derived from the grain.   Knowing that, you can increase the?alcohol by volume (ABV)?by increasing the size of the grain bill or increasing the amount of malt extract used.Though, this method can completely?change the recipe if all other factors remain the same, so a popular method for increasing the ABV of an existing beer recipe without bringing much change, 
is to simply add more sugar into the mix.

# GitHub address:

https://github.com/guvp2017/DDS_Case-Study-01.git